The Hot Hand Fallacy in Call of Duty

### 2022-08-23 paper/paper.Rmd
footnote about number of sequences

@@

In Table \ref{tbl:cod-runs}, the observed and expected count of sequences, $N^{\zeta r}$ and $\hat{N}^{\zeta r}$ respectively, are shown for sequences, $\zeta(r)$, for which one can reject the Wald-Wolfowitz null hypothesis at a confidence level of $\alpha = 0.05$, for $r \in [8, 9, 10]$. In addition to the 13 sequences shown, there are 12 additional sequences for $r = 11$.

@@

Further regarding future work, we have contacted the Twitter user "R11stats", who privately tracks in-round player engagements.[^26] R11stats expressed intent on making the data public, which would allow for research into player-specific momentum. While it seems there is no team-level hot hand effect in CoD SnD, perhaps there is with eliminations performed by individual players.

[^26]: <https://twitter.com/R11stats>

>>>>

# bind_rows(
#   cod_round_arrangements_naive |> 
#     filter(is_significant) |> 
#     transmute(ws, is_naive = TRUE),
#   cod_round_arrangements_naive |> 
#     filter(is_significant) |> 
#     transmute(ws, is_naive = FALSE)
# ) |> 
#   count(ws) |> 
#   filter(n == 1L)

@@

In Table \ref{tbl:cod-runs}, the observed and expected count of sequences, $N^{\zeta r}$ and $\hat{N}^{\zeta r}$ respectively, are shown for sequences, $\zeta(r)$, for which one can reject the Wald-Wolfowitz null hypothesis, given probability of Bernoulli trial success $\phi = 0.575$,[^26] at a confidence level of $\alpha = 0.05$, for $r \in [8, 9, 10]$. In addition to the 13 sequences shown, there are 12 additional sequences for $r = 11$.

[^26]: If we used $\phi = 0.5$, we would get the same exact seqeunces.

@@

Further regarding future work, we have contacted the Twitter user "R11stats", who privately tracks in-round player engagements.[^27] R11stats expressed intent on making the data public, which would allow for research into player-specific momentum. While it seems there is no team-level hot hand effect in CoD SnD, perhaps there is with eliminations performed by individual players.

[^27]: <https://twitter.com/R11stats>

### 2022-08-23 paper/paper.tex
footnote about number of sequences

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Both have economic aspects that can create clear advantages for one
  team in a round, given how prior rounds played out. CoD has no such
  equivalent, except for perhaps ``kill streaks'', which infrequently
  occur.
\item
  Teams play either offense or defense for many consecutive rounds. (The
  former has a 15-15-1 format and the latter uses a 12-12-1 format.) On
  the other hand, teams in CoD SnD rotate roles every round, analogous
  to a 1-1-1-1-1-1-1 format for home advantage in best-of-seven series
  for professional sports like the MLB, NBA, and NHL.\footnote{1-1-1-1-1-1-1
    is not used today in these leagues, but it was at least once in each
    league.} While theoretically one might be able to account for any
  kind of format, such as a 5-5-1, the rotation of team sides every
  round is convenient for convincing ourselves that rounds could
  reasonably be modeled as i.i.d. Bernoulli trials.
\item
  Both Counter-Strike and Valorant have overtime rules---team must win
  by two rounds---which can make end-of-series sequences difficult to
  model. CoD SnD does not have overtime rules.
\end{enumerate}

@@

In Table \ref{tbl:cod-runs}, the observed and expected count of
sequences, \(N^{\zeta r}\) and \(\hat{N}^{\zeta r}\) respectively, are
shown for sequences, \(\zeta(r)\), for which one can reject the
Wald-Wolfowitz null hypothesis at a confidence level of
\(\alpha = 0.05\), for \(r \in [8, 9, 10]\). In addition to the 13
sequences shown, there are 12 additional sequences for \(r = 11\).

@@

Further regarding future work, we have contacted the Twitter user
``R11stats'', who privately tracks in-round player
engagements.\footnote{\url{https://twitter.com/R11stats}} R11stats
expressed intent on making the data public, which would allow for
research into player-specific momentum.

>>>>

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Both have economic aspects that can create clear advantages for one
  team in a round, given how prior rounds played out. CoD has no such
  equivalent, except for perhaps ``score streaks'', which infrequently
  occur.
\item
  Teams play either offense or defense for many consecutive rounds. (The
  former has a 15-15-1 format and the latter uses a 12-12-1 format.) On
  the other hand, teams in CoD SnD rotate roles every round, analogous
  to a 1-1-1-1-1-1-1 format for home advantage in best-of-seven series
  for professional sports like the MLB, NBA, and NHL.\footnote{1-1-1-1-1-1-1
    is not used today in these leagues, but it was at least once in each
    league.} While theoretically one might be able to account for any
  kind of format, such as a 5-5-1, the rotation of team sides every
  round is convenient for convincing ourselves that rounds could
  reasonably be modeled as i.i.d. Bernoulli trials.
\item
  Both Counter-Strike and Valorant have overtime rules---team must win
  by two rounds---which can make end-of-series sequences difficult to
  model. CoD SnD does not have overtime rules.
\end{enumerate}

@@

In Table \ref{tbl:cod-runs}, the observed and expected count of
sequences, \(N^{\zeta r}\) and \(\hat{N}^{\zeta r}\) respectively, are
shown for sequences, \(\zeta(r)\), for which one can reject the
Wald-Wolfowitz null hypothesis, given probability of Bernoulli trial
success \(\phi = 0.575\),\footnote{If we used \(\phi = 0.5\), we would
  get the same exact seqeunces.} at a confidence level of
\(\alpha = 0.05\), for \(r \in [8, 9, 10]\). In addition to the 13
sequences shown, there are 12 additional sequences for \(r = 11\).

@@

Further regarding future work, we have contacted the Twitter user
``R11stats'', who privately tracks in-round player
engagements.\footnote{\url{https://twitter.com/R11stats}} R11stats
expressed intent on making the data public, which would allow for
research into player-specific momentum. While it seems there is no
team-level hot hand effect in CoD SnD, perhaps there is with
eliminations performed by individual players.
